### 2010-12-08 docs/tex/review.tex
New image update.
Some minor changes...

\begin{quote}
\textsl{`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature. Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts. The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment." - Christopher G. Langton}
\end{quote}

@@

The field of Artificial Life (AL) has been described by Taylor as a tool for biological inquiry \cite{taylor1993}. While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.

@@

\subsubsection{Criteria}
Echo has been constructed on a certain set of criteria. The following is a short summary on it extracted from \cite{holland1996}.

\begin{itemize}
	\item Simplicity is considered as the first and foremost criteria. Instead of emulating a real system Echo is more of a thought experiment. Simplicity is attained by carefully constraining agent interaction and also giving the agents only a primitive internal model. 
	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting, while mobility is also part of a wide range of geographical setting. Input to the environment which are considered as stimuli or resource can also be diversified. 
	\item Fitness of each of the agents is an evolving criteria. Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents. Instead of being a constant value it should evolve along with the system. 
	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}. Interpretation of results from the Echo model should be direct and ready-made. As simulation is nothing but manipulation of numbers and symbols, it is always possible to make fanciful and deceiving interpretation of them, taking the opportunity to prove one's point. So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation. 5
	\item 
	\item 
\end{itemize}

@@

\paragraph{Criteria}

>>>>

\begin{quote}
\textsl{`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature. Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts. The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."}
\end{quote}

The field of Artificial Life (AL) has been described by Taylor also as a tool for biological inquiry \cite{taylor1993}. While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.

@@

@@

\subsubsection{Criteria}
Echo has been constructed on a certain set of criterion. The following is a short summary on it extracted from Holland's, \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.

\begin{itemize}
	\item Simplicity is considered as the first and foremost criteria. Instead of emulating a real system Echo is more of a thought experiment. Simplicity is attained by carefully constraining agent interaction and also giving the agents only a primitive internal model. 
	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting, while mobility is also part of a wide range of geographical setting. Input to the environment which are considered as stimuli or resource can also be diversified. 
	\item Fitness of each of the agents is an evolving criteria. Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents. Instead of being a constant value it should evolve along with the system. 
	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}. Interpretation of results from the Echo model should be direct and ready-made. As simulation is nothing but manipulation of numbers and symbols, it is always possible to make fanciful and deceiving interpretation of them, taking the opportunity to prove one's point. So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation. 
	\item 
	\item 
\end{itemize}

@@
